A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-10-11 rebuttal/rebuttal.md

### Reviewer #9B

#### Explicit Questions

##### Major Issues

1. The description of the programming task is somewhat vague and it is unclear
   if it went through any validation for appropriateness to measure students'
   ability. What was the exact task (the authors mention the Mandelbrot Set
   they provided as an example, but do not expand on their "simple problem").
   There is no way for the reader to determine how appropriate this task was
   without knowing the problem, so perhaps listing the question/problem itself
   would be best. (TODO: Pedro)
2. The reviewer assumes that the programming assignment and questionnaires were
   solo activities. However, this was not explicitly described. (Since the
   authors described this course as a place where undergraduate students and
   graduate students could share their knowledge). (TODO: Alfredo)
3. How were the questions developed, and what measures did the authors take to
   make sure they were appropriate to measure what they wanted to measure? (DONE)
4. Were the questions listed in Portuguese (the reviewer believes this might be
   an option as this study took place in Brazil) or English? (TODO: Pedro)
5. Some of the questions in Table 1 are vague and the students might interpret
   them in different ways. For example, what level of commitment/experience
   does "Had contact with the APIs before?" assume? What does "the API" mean?
   The same question goes for what "learned" means in the following two
   questions.(DONE)
6. In Table 3, what is the difference between questions 2 and 3? "Was simpler
   to use" vs. "Was easier to use". (TODO: Pedro)
7. The reviewer does not believe that the major finding of this paper is
   accurately described and cannot agree with the author's statement in the
   conclusion that 52.2% of students performing better using Pthreads
   constitutes a "majority." (TODO: Pedro, mas acho que se pensarmos juntos mitigaremos)

@@

##### Minor Issues

1. Some of the statements in the introduction and the descriptions of OpenMP
   and Pthreads can use additional references (e.g., "slowdowns on Moore's law
   and the end of Dennard scaling"). (TODO: Raphael)
2. Recommend changing "Listing X" to "Figure X". (DONE)
3. Recommend displaying "Listing 1" in one column instead of splitting it in
   the middle. (DONE)
4. Recommend using active voice instead of passive voice (e.g., "Different
   approaches have been proposed to study..." (DONE)
5. Recommend not using colors for Figures since some readers might not be able
   to distinguish them (or someone might print it out in black-and-white). (TODO: Pedro, relacionado com item 4 do revisão 1)
6. Table 1. The second question has a typo "Had contat [sic] with the API///" (DONE)

### 2017-10-16 sections/01-introduction.tex
Added reference requested

Multi-core architectures became essential and ubiquitous for High-Performance
Computing in the last decade, their relevance increased by recent slowdowns on
Moore's law and the end of Dennard scaling.  Selecting the appropriate tool for
programming multi-core architectures is also essential, since it is necessary
to program a multi-core architecture effectively to leverage its performance.

>>>>

Multi-core architectures became essential and ubiquitous for High-Performance
Computing in the last decade, their relevance increased by recent slowdowns on
Moore's law and the end of Dennard scaling \cite{esmaeilzadeh2012dark}.
Selecting the appropriate tool for programming multi-core architectures is also
essential, since it is necessary to program a multi-core architecture
effectively to leverage its performance.
